Bound within Boundaries: How Well Do Protected Areas Match Movement Corridors of Their Most Mobile Protected Species?

### 2021-03-08 Chapter_0/04_Manuscript/Manuscript.tex
Minor modifications

\section{Methods}
\subsection{Study Area}
The study area (centered at -17\degree 13'9''S, 23\degree 56'4''E;
\Cref{StudyArea}a) was outlined by a rectangular bounding box stretching over
1.3 Mio km\textsuperscript{2} and encompassing the entire KAZA-TFCA
(\Cref{StudyArea}b). The KAZA-TFCA lies in the basins of the Okavango and
Zambezi rivers and includes parts of Angola, Botswana, Namibia, Zimbabwe, and
Zambia. With a total area of over 520'000 km\textsuperscript{2} it constitutes
the earth's largest transboundary conservation area and is characterized by
diverse landscapes, including savanna, grassland, and dry or moist woodland
habitats. Rainfall in the study area is seasonal and lasts from November to
March. The KAZA-TFCA also comprises the Okavango Delta, which represents a
highly dynamic hydrological flood-pulsing system \citep{McNutt.1996,
Wolski.2017}. The extent of the flood in the delta greatly changes within and
between years, depending on the amount of rain that descends from the catchment
areas in Angola and reaches the distal ends of the delta between July and August
(Figure S4). The flood drastically affects surrounding landscapes, so that
during maximum extent (ca. 12'000 km\textsuperscript{2}) the delta becomes a
patchy conglomerate of swamps, open water, and islands, whereas these structures
run dry when the flood retracts to its minimum extent (ca. 5'000
km\textsuperscript{2}; \citealp{Wolski.2017}). Despite 36 national parks (NPs)
and other protected areas, there is considerable human influence in some regions
of the KAZA-TFCA, mainly originating from farms, human density, and road
traffic.

@@

\section{Data Availability}
GPS movement data of dispersing coalitions is available in the Dryad Digital
Repository doi:10.5061/dryad.dncjsxkzn \citep{Hofmann.2021}. R-code showcasing
the main steps for sections 2.5 to 2.6 can be obtained through GitHub
(\url{https://github.com/DavidDHofmann/LeastCostAnalysis}).

>>>>

\section{Materials and Methods}
\subsection{Study Area}
The study area (centered at -17\degree 13'9''S, 23\degree 56'4''E;
\Cref{StudyArea}a) was outlined by a rectangular bounding box stretching over
1.3 Mio km\textsuperscript{2} and encompassing the entire KAZA-TFCA
(\Cref{StudyArea}b). The KAZA-TFCA lies in the basins of the Okavango and
Zambezi rivers and includes parts of Angola, Botswana, Namibia, Zimbabwe, and
Zambia. With a total area of over 520'000 km\textsuperscript{2} it constitutes
the earth's largest transboundary conservation area and is characterized by
diverse landscapes, including savanna, grassland, and dry or moist woodland
habitats. Rainfall in the study area is seasonal and lasts from November to
March. The KAZA-TFCA also comprises the Okavango Delta, which represents a
highly dynamic hydrological flood-pulsing system \citep{McNutt.1996,
Wolski.2017}. The extent of the flood in the delta greatly changes within and
between years, depending on the amount of rain that descends from the catchment
areas in Angola and reaches the distal ends of the delta between July and August
(Figure S4). The flood drastically affects surrounding landscapes, so that
during maximum extent (ca. 12'000 km\textsuperscript{2}) the delta becomes a
patchy conglomerate of swamps, open water, and islands, whereas these structures
run dry when the flood retracts to its minimum extent (ca. 5'000
km\textsuperscript{2}; \citealp{Wolski.2017}). Despite 36 national parks (NPs)
and other protected areas, there is considerable human influence in some regions
of the KAZA-TFCA, mainly originating from farms, human density, and road
traffic.

@@

\section{Data Availability Statement}
GPS movement data of dispersing coalitions available via the Dryad Digital
Repository doi:10.5061/dryad.dncjsxkzn \citep{Hofmann.2021}. R-code showcasing
the main steps for sections 2.5 to 2.6 can be obtained through GitHub
(\url{https://github.com/DavidDHofmann/LeastCostAnalysis}).
